---
title: "Objects in R"
author: "Ahmed Tawfik"
date: "September 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R has five basic or "atomic" classes of objects: character, numberic, integer, logical, complex

We can know the class of the object using the class funciton.
There is also the mode function which returns the mode of R objects.

```{r}
character.obj <- 'a'
class(character.obj) # "character"
mode(character.obj) # "character"

string.obj <- "abc" # String is considered as characters in R
class(string.obj) # "character"
mode(string.obj) # "character"

num.obj <- 2
class(num.obj) # "numeric"
mode(num.obj) # "numeric"

int.obj <- as.integer(num.obj) #numeric is the default, we have to use as.integer function to create integer objects
class(int.obj) # "integer"
mode(int.obj) # "numeric" , still R will treat is as numeric during the computations


logical.obj <- TRUE
class(logical.obj) # "logical"
mode(logical.obj) # "logical"

complex.obj <- 1+2i
class(complex.obj) # "complex"
mode(complex.obj) # "complex"


```

Alternative ways to test the object mode using is.numeric(), is.charater(), and is.logical(), etc..
```{r}
is.numeric(num.obj) # TRUE
is.logical(num.obj) # FALSE
is.character(string.obj) # TRUE
```

The function object could be also checked using the class and mode functions
```{r}
mean(c(3,4,6,7)) # 5
class(mean) # "function"
mode(mean) # "function"
is.function(mean) # TRUE
```





